Incentivizing Exploration with Unbiased History

### 2018-10-25 2level.tex
stuff

\begin{theorem}
\label{thm:2level}
With proper setting of $T_1$, the 2-level policy gets expected regret
$O(T^{2/3} \log(T)^{1/3})$. If we know the gap between the means of
the best arm and second best arm is larger than $\Delta$, we can make
the expected regret $O(\log(T) \cdot \Delta^{-2})$.
\end{theorem}

@@

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution Ber$(\mu_a)$. Then for each arm $a$ and any
$N\in [T]$, we can think of the sequence of the first $N$ realized
rewards of $a$ coming from the prefix of $N$ cells in its reward
tape. Define $W^{a,t}_2$ to be the event that the empirical mean of
the first $t$ \swedit{realized rewards in the tape} of arm $a$ is at
most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be
the intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).
By Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.

Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.
\end{proof}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\begin{theorem}
\label{thm:2level}
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, the 2-level policy gets
expected regret $O(T^{2/3} \log(T)^{1/3})$.
\end{theorem}

@@

% \begin{itemize}
  \OMIT{\paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$.}
  Define $W_1^a$ to be the event that the number of arm $a$ pulls in
  the first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.} 
\OMIT{  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
}
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By Lemma~\ref{lem:t1runs}, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\OMIT{\paragraph{Concentration of the empirical mean of arm $a$ pulls
    in the first level.}}  Next, we show that the empirical mean of
each arm $a$ is close to the true mean. To facilitate our reasoning,
let us imagine there is a tape of length $T$ for each arm $a$, with
each cell containing an independent draw of the realized reward from
the distribution $\cD_a$. Then for each arm $a$ and any $N\in [T]$, we
can think of the sequence of the first $N$ realized rewards of $a$
coming from the prefix of $N$ cells in its reward tape. Define
$W^{a,t}_2$ to be the event that the empirical mean of the first $t$
\swedit{realized rewards in the tape} of arm $a$ is at most
$\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$ to be the
intersection of these events (i.e.  $\bigcap_{a,t} W^{a,t}_2$).  By
Chernoff bound,\swcomment{$t$ may be confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

@@

For any arm $a$ and agent $t$ in the second level, by $W_1$ and $W_2$, we have
\[
|\bar{\mu}^t_a - \mu_a| \leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}.
\]
By $W_1$ and Assumption \ref{ass:embehave}, we have
\[
|\bar{\mu}^t_a - \hat{\mu}^t_a| \leq \frac{c_m}{\sqrt{q_aT_1/2}}.
\]
Therefore,
\[
|\hat{\mu}^t_a - \mu_a|\leq \sqrt{\frac{2\log(T)}{q_aT_1 /2}}+\frac{c_m}{\sqrt{q_aT_1/2}} \leq 3 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
So the second-level agents will pick an arm $a$ which has $\mu_a$ at most $6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$ away from $\mu_1$. To sum up, the total expected regret is at most 
\[
T_1 \cdot \GdT + T \cdot (1-\Pr[W_1 \cap W_2]) + T \cdot  6 \sqrt{\frac{\log(T)}{\GdP T_1 }}.
\]
By setting $T_1 = T^{2/3}\log(T)^{1/3}$, we get expected regret $O(T^{2/3}\log(T)^{1/3})$.
\OMIT{Notice that if we know the gap parameter is known to be larger than
$\Delta$, we can set
\[
T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2 \cdot p_G} \log(T) \right).
\]
In this case, since $\Delta \geq 6 \sqrt{\frac{\log(T)}{\GdP T_1 }}$, we know agents in the second level will all pull arm 1. Therefore, the total expected regret is at most
\[
T_1 \cdot \GdT + T \cdot (1- \Pr[W_1 \cap W_2]) = O(\Delta^{-2} \log(T)).
\]
This completes the proof.}
\end{proof}

\begin{remark}
  If the gap parameter $\Delta$ is known to the principal, we can set
  $T_1 = \max\left( \frac{4\GdT^2}{\GdP^2}\log(T), \frac{36 }{\Delta^2
      \cdot p_G} \log(T) \right)$, and achieves an expected regret of
  $O(\log(T) \cdot \Delta^{-2})$.
\end{remark}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2018-10-25 3level.tex
stuff

In the proof, we need not only the concentration argument as the
2-level recommendation policy, but also the anti-concentration
argument to show that agents explore more in the second round if
$\mu_1-\mu_2$ is not too big.

\iffalse
Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
parallel. The second level also has $S$ groups of agents. Each group
has $T_2$ agents and they observe the history of corresponding group
in the first level. All the rest agents are in the third level and
they observe the entire history of the first two levels.  See also
Figure \ref{fig:3level} for a graphical view of the information flow.

@@

\end{tikzpicture}
\caption{Structure of the information graph for the 3-level
  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
  length $T_G$. The sub-history of each red box is then aggregated and
  sent to a corresponding purple box of agents in level 2. Then the
  entire history of levels 1 and 2 is aggregated and shown to all
  agents in level 3.}
\label{fig:3level}
\end{figure}
\swcomment{check the figure caption above. can we index the indicate
  there are $S$ groups in the figure?}

\begin{lemma}[``Clean'' events]

\end{lemma}

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound,\swcomment{a bit confused about what $t_1$ and $t_2$ mean?}
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]

Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). By union bound, we have
\[
\Pr[W_2] \geq 1- \frac{4S}{T^2}.
\]

\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}

@@

\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}

Consider the tapes defined in the second bullet again. For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{itemize}

>>>>

\iffalse
In the proof, we need not only the concentration argument as the
2-level recommendation policy, but also the anti-concentration
argument to show that agents explore more in the second round if
$\mu_1-\mu_2$ is not too big.

Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
parallel. The second level also has $S$ groups of agents. Each group
has $T_2$ agents and they observe the history of corresponding group
in the first level. All the rest agents are in the third level and
they observe the entire history of the first two levels.  See also
Figure \ref{fig:3level} for a graphical view of the information flow.

@@

\end{tikzpicture}
\caption{Structure of the information graph for the 3-level
  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
  length $T_G$. The sub-history of each red box is then aggregated and
  sent to a corresponding purple box of agents in level 2. Then the
  entire history of levels 1 and 2 is aggregated and shown to all
  agents in level 3.}
\label{fig:3level}
\end{figure}
% \swcomment{check the figure caption above. can we index the indicate
%   there are $S$ groups in the figure?}

\subsection{Clean events}
We will first establish four \emph{clean events} that together occur
with probability at least $1 - O(1/T)$. The first one says that every
group of \ALGG runs in the first level ensures that each arm $a$ is
pulled at least $\Omega(T_1)$ times, which follows from
Lemma~\ref{lem:t1runs} and union bound.

\begin{lemma}[Concentration of first-level number of pulls.]
  Let $W_1$ be the event that for all groups $s\in [S]$ and arms
  $a\in \{1, 2\}$, the number of arm $a$ pulls in the $s$-th
  first-level group is in the range of
  $$
  \left[q_a T_1- \GdT \sqrt{T_1\log(T)}, q_a T_1 + \GdT \sqrt{T_1\log(T)}\right],
  $$
  where $q_a$ is the expected number of arm $a$ pulls in a $\ALGG$ run
  of length $T_G$. Then $\Pr[W_1] \geq 1- \frac{4S}{T^2}$.
\end{lemma}

\begin{proof}
  For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
  that the number of arm $a$ pulls in the $s$-th first-level group is
  between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
  $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Let $W_1$  be the intersection of all these events (i.e.
$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\swcomment{let's put this in appendix.}
\end{proof}

The next two events are about the distribution of the mean rewards in
the first level. To state the events, it will be useful to think of a
hypothetical reward tape tape $\cT_{s, a}$ of length $T$ for each
group $s$ and arm $a$, with each cell independently sampled from
$\cD_a$.  The tape encodes rewards as follows: the $j$-th time arm $a$
is chosen by the group $s$ in the first level, its reward is taken
from the $j$-th cell in this arm’s tape. We now show the concentration
behavior of the mean rewards across all consecutive pulls among all
such tapes.

\begin{lemma}[Concetration of empirical means]
  For any $t_1, t_2\in [T]$ such that $t_1 < t_2$, $s\in [S]$, and
  $a\in \{1,2\}$, let $W_2^{s,a,t_1,t_2}$ be the event that the mean
  among the cells indexed by $t_1, (t_1+1), \ldots, t_2$ in the tape
  $\cT_{a, s}$ is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away
  from $\mu_a$.  Let $W_2$ be the intersection of all these events
  (i.e.  $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). Then
  \[
    \Pr[W_2] \geq 1- \frac{4S}{T^2}.
  \]
\end{lemma}

\begin{proof}
  By Chernoff bound,
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
By union bound, we have
\[
\Pr[W_2] \geq 1- \frac{4S}{T^2}.
\]
\end{proof}

\begin{lemma}[Anti-concentration of empirical means]
  For any $s\in [S]$, any arm $a$, let $\tilde\mu_{a,s}$ be the
  empirical mean of the first $q_a T_1$ cells in tape $\cT_{a, s}$.
  Let $W_4^{s,a,high}$ be the event
  $\tilde\mu_{a, s} \geq \mu_a + 1/\sqrt{q_a T_1}$ and let
  $W_4^{s,a,low}$ be the event that
  $\tilde\mu_{a, s} \leq \mu_a - 1/\sqrt{q_a T_1}$.  Let $W_4$ be
  $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$.
  \[
    \Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
  \]
\end{lemma}

\begin{proof}
By Berry-Essen Theorem and
  $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent
across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]
\end{proof}

\subsection{Case Analysis}

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\OMIT{
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
\OMIT{By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,}
For the $s$-th first-level group, define $W_1^{a,s}$ to be the event
that the number of arm $a$ pulls in the $s$-th first-level group is
between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and
$q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Lemma~\ref{lem:t1runs}
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Let $W_1$  be the intersection of all these events (i.e.
$W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]}

\OMIT{\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound,\swcomment{a bit confused about what $t_1$ and $t_2$ mean?}
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]

Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{a,s,t_1,t_2} W_2^{s,a,t_1,t_2}$). By union bound, we have
\[
\Pr[W_2] \geq 1- \frac{4S}{T^2}.
\]
}
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first two levels:}

@@

\OMIT{\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}

Consider the tapes defined in the second bullet again. For the $s$-th first-level group and arm $a$, define $W_4^{s,a,high}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1}$ and define  $W_4^{s,a,low}$  to be the event that first $q_a T_1$ pulls of arm $a$ in the corresponding tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1}$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{s,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{s,a,low}] > 1/4.
\]
Since $W_4^{s,a,high}$ is independent with $W_4^{s,3-a,low}$, we have
\[
\Pr[W_4^{s,a,high} \cap W_4^{s,3-a,low}] =\Pr[W_4^{s,a,high}] \cdot  \Pr[W_4^{s,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W_4$ as $\bigcap_a \bigcup_s (W_4^{s,a,high} \cap W_4^{s,3-a,low})$. Notice that $(W_4^{s,a,high} \cap W_4^{s,3-a,low})$ are independent across different $s$'s. By union bound, we have
\[
\Pr[W_4] \geq 1- 2(1-1/16)^S \geq 1 -2 /T.
\]}
\end{itemize}

### 2018-10-25 model.tex
stuff

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$. At each round $t\in [T]$, a new agent $t$ arrives,
receives a message $m_t$ from the principal, chooses an arm
$a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is
immediately observed by the principal. Given any sequence of arms
$\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is
defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

>>>>

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution $\cD_a$ with an
unknown mean $\mu_a$. At each round $t\in [T]$, a new agent $t$
arrives, receives a message $m_t$ from the principal, chooses an arm
$a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is
immediately observed by the principal. Given any sequence of arms
$\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is
defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]
